% !TEX root = paris_koloveas-cv.tex
%
\nohyphens{\color{gray}{Publications}} 
& S. Chatzopoulos, \underline{P. Koloveas}, K. Vichos, T. Vergoulis, \textbf{Easing the burden of creating and managing narrative CVs in academia \textit{(Poster)}}, \textit{In the World Conference on Research Integrity (WCRI), Athens, Greece, June 2024.} \\
& \\ [-5pt]

& \underline{P. Koloveas}, S. Chatzopoulos, C. Tryfonopoulos, and T. Vergoulis, \textbf{BIP! NDR (NoDoiRefs): A Dataset of Citations from Papers Without DOIs in Computer Science Conferences and Workshops}, \textit{In the 27th International Conference on Theory and Practice of Digital Libraries (TPDL), Zadar, Croatia, September 2023.} \\
&  \\ [-5pt]
% &  \\

% & \textbf{BIP! NDR (NoDoiRefs): A Dataset of Citations from Papers Without DOIs in Computer Science Conferences and Workshops} \\
% & P. Koloveas, S. Chatzopoulos, and C. Tryfonopoulos, and T. Vergoulis. \\
% & \textit{In the 27th International Conference on Theory and Practice of Digital Libraries (TPDL), Zadar, Croatia, Sep 2023.} \\
% & \\[-5pt]

& G. Fotopoulos, \underline{P. Koloveas}, P. Raftopoulou, and C. Tryfonopoulos, \textbf{Comparing Data Store Performance for Full-Text Search: to SQL or to NoSQL?}, \textit{In the 12th International Conference on Data Science, Technology and Applications (DATA), Rome, Italy, July 2023.} \\
& \\[-5pt]

% & \textbf{Comparing Data Store Performance for Full-Text Search: to SQL or to NoSQL?} \\
% & G. Fotopoulos, P. Koloveas, P. Raftopoulou, and C. Tryfonopoulos. \\
% & \textit{In the 12th International Conference on Data Science, Technology and Applications (DATA), Rome, Italy, July 2023.} \\
% & \\[-5pt]
% \newpage

& \underline{P. Koloveas}, T. Chantzios, C. Tryfonopoulos, and S. Skiadopoulos, \textbf{Cyber-Threat Intelligence \textit{(Book Chapter)}}, \textit{Security Technologies and Methods for Advanced Cyber Threat Intelligence, Detection and Mitigation, Now Publishers, 2022}. \\
& \\ [-5pt]

% & \underline{P. Koloveas}, T. Chantzios, S. Alevizopoulou, C. Tryfonopoulos, and S. Skiadopoulos, \textbf{inTIME:\@ A Machine Learning-Based Framework for Gathering and Leveraging Web Data to Cyber-Threat Intelligence}, \textit{In: MDPI Electronics, Special issue on ``Advances on Networks and Cyber Security'', March 2021.} \\
% & \\[-5pt]

& \underline{P. Koloveas}, T. Chantzios, S. Alevizopoulou, C. Tryfonopoulos, and S. Skiadopoulos, \textbf{inTIME:\@ A Machine Learning-Based Framework for Gathering and Leveraging Web Data to Cyber-Threat Intelligence}, \textit{In: MDPI Electronics, Special issue on ``Advances on Networks and Cyber Security'', March 2021.} \\
& \\[-5pt]

% & \textbf{inTIME:\@ A Machine Learning-Based Framework for Gathering and Leveraging Web Data to Cyber-Threat Intelligence} \\
% & P. Koloveas, T. Chantzios, S. Alevizopoulou, C. Tryfonopoulos, and S. Skiadopoulos.\\
% & \textit{MDPI Electronics, Special issue on ``Advances on Networks and Cyber Security'', March 2021.} \\
% & \\[-5pt]

& S. Alevizopoulou, \underline{P. Koloveas}, C. Tryfonopoulos, P. Raftopoulou, \textbf{Social Media Monitoring for IoT Cyber-Threats}, \textit{In the Workshop on Data Science for Cyber Security (DS4CS @ IEEE CSR), Rhodes, Greece, July 2021.}\\
& \\[-5pt]

% \newpage
% & \textbf{Social Media Monitoring for IoT Cyber-Threats} \\
% & S. Alevizopoulou, P. Koloveas, C. Tryfonopoulos, P. Raftopoulou. \\
% & \textit{In the Workshop on Data Science for Cyber Security (DS4CS @ IEEE CSR), Rhodes, Greece, July 2021.}\\
% & \\[-5pt]

& \underline{P. Koloveas}, T. Chantzios, C. Tryfonopoulos, and S. Skiadopoulos, \textbf{A crawler for harvesting the clear, social, and dark web for IoT-related Cyber-Threat Intelligence}, \textit{In the IEEE Workshop on Cyber Security \& Resilience in the Internet of Things (CSRIoT@IEEE Services), Milan, Italy, July 2019.}\\
& \\[-5pt]

% & \textbf{A crawler for harvesting the clear, social, and dark web for IoT-related Cyber-Threat Intelligence} \\
% & P. Koloveas, T. Chantzios, C. Tryfonopoulos, and S. Skiadopoulos.\\
% & \textit{In the IEEE Workshop on Cyber Security \& Resilience in the Internet of Things (CSRIoT@IEEE Services), Milan, Italy, July 2019.}\\
% & \\[-5pt]

& T. Chantzios, \underline{P. Koloveas}, S. Skiadopoulos, N. Kolokotronis, C. Tryfonopoulos, V. Bilali, and D. Kavallieros, \textbf{The quest for the appropriate Cyber-Threat Intelligence sharing platform}, \textit{In the 8th International Conference on Data Science, Technology and Applications (DATA), Prague, Czech Republic, July 2019.}\\
% & \\

% & \\
% & \textbf{Title of your third most recent research paper} \\
% & First author, second author, third author, fourth author. \\
% & \textit{Journal of something or the other, 2020.}\\
% & \\